Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
removed 1 discussion comment

<!--FOLLOWING SENTENCES SHOULD GO IN DISCUSSION
For an n-dimensional point cloud, up to n-1 feature dimensions can be calculated. 
In the field, most work has only included calculations up to 1 or 2 feature dimensions.
Perhaps this is due to difficulty of conceptualizing what high dimensional features represent. 
However, it might also be due to computational restrictions of calculating high dimensional features.-->
Large data and feature dimensionality often restricts persistent homology calculations to small point clouds due to computational limits.
When calculating persistent homology on a high-dimensional point cloud, as Vietoris-Rips feature dimension increases, there is a corresponding increase in runtime (Figure \ref{fig:box}).
Dionysus is clearly outmatched by GUDHI and Ripser as feature dimension increases, with the difference being clearest for larger point clouds; by feature dimension 5, Ripser outpaces GUDHI as well (Figure \ref{fig:box}).
Due to the limited number of points, it is unclear whether runtime for each library grows polynomially or exponentially.
<!--RECHECK, should be enough data point to regress on-->

>>>>

Large data and feature dimensionality often restricts persistent homology calculations to small point clouds due to computational limits.
When calculating persistent homology on a high-dimensional point cloud, as Vietoris-Rips feature dimension increases, there is a corresponding increase in runtime (Figure \ref{fig:box}).
Dionysus is clearly outmatched by GUDHI and Ripser as feature dimension increases, with the difference being clearest for larger point clouds; by feature dimension 5, Ripser outpaces GUDHI as well (Figure \ref{fig:box}).
Due to the limited number of points, it is unclear whether runtime for each library grows polynomially or exponentially.
<!--RECHECK, should be enough data point to regress on-->
